\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-25 draft.tex
Tried to add an explanation on the output in the loop

>>>>

%-----------------------------------------------------------------------------
\paragraph{A note on dealing with output in the main loop.} 
%-----------------------------------------------------------------------------

So far we have assumed that there was no output in the main loop and mentioned
that this restriction is lifted in J-ReCoVer. Due to space restrictions, a
proper explanation of the way of handling this issue is beyond the scope of this
paper, but we give at least a brief sketch of the solution. In particular, the
Preprocessor performs one more transformation which adds an assignment $v := e$
for every $out(e)$ statement in the main loop where $v$ is a fresh variable
assigned just once in the loop body. This makes the output visible for our
analysis since $v$ appears in Formula~\ref{eq:commu}. The Prover then makes an
additional check whether the value of $F(n, x_1,x_2,\ldots,x_k)$ projected on
$v$ stays the same for any input value $n$ and any initial values of the
variables $x_i$.
